---
title: "Razan-TMreview"
author: "Razan Alsayed Omar"
date: '2022-03-20'
output: html_document
---

################################################################################
Review:

1. Great data inspection, nicely organized
2. For file size, try installing this package - it will take a while:
```{r}
install.packages("remotes")
remotes::install_github("skgrange/threadr")
```

This will allow you to use the following function:
```{r}
file_size(file, unit = "mb")
```
File is the file name you want to inspect, unit is the measurement unit for the file size, mb is megabytes.

3. Great job on the data processing.
4. Your code for data visualization is missing. You haven't included the code for visualizing missing data and heterozygosity or your own visualization. Please make sure to complete this as it's a huge part of the assignment is missing. I'm happy to be of help and give you some ideas. 
5. Most importantly, your code is working just fine for me. 
################################################################################
